### 2012-11-12 doc/progress_plan/report.tex
pretty much done intro and started lit review

The Partridge project has been underway since the beginning of October. The
following section looks at related works and how Partridge compares to them,
some prior investigation and prototyping work that has already been carried
out.

@@

There are also a number of search and indexing systems that specifically look
for scientific papers as opposed to web pages. One of the most publicised and
well known paper search system is Google Scholar
(\url{http://scholar.google.com}).  As can be seen in Figure
\ref{fig:scholar_basic}, This is an adaptation of Google's general search
engine (discussed above) to specifically index and search scientific papers.
Google also offers advanced query options specific to Scholar that allow
searching by author, year and for words that occur only in the document title
as shown in figure \ref{fig:scholar_advanced}. Whilst this does deal with the
problem of `information overload' and provides even more fine control over the
information returned from searches,  the user is still required to have a very
good idea of what they are looking for in terms of keywords and/or specific
authors. It is possible that a user would not know what they are looking for
until they've seen it.

@@

Partridge will provide the option to filter papers by subject and it is hoped
that the system will also provide user-specific recommendations by profiling
them through their reading history. This will make it easier for users to find
relevant papers without knowing exactly what keywords they want to search for.

>>>>

The Partridge project has been underway since the beginning of October. The
following section looks at some literature on the subjects of Natural Language
Processing and information retrieval within the domain of scientific papers.
Some related works are investigated and compared to Partridge and details of
prototyping work that has been carried out are given.

\subsection{Literature Review}
Natural Language Processing is still a relatively unexplored discipline and as
such is still a very active area of research and development within the
Artificial Intelligence community. E. Liddy defines Natural Language Processing as:

\begin{quotation} 
A theoretically motivated range of computational techniques for analyzing and
representing naturally occurring texts at one or more levels of linguistic
analysis for the purpose of achieving human-like language processing for a
range of tasks or applications. \cite{liddy2001natural} 
\end{quotation}

In the case of Partridge, scientific papers, constituting the naturally occuring
texts, are processed at sentence-by-sentence and word-by-word levels of
linguistics and represented in the form of Extended Markup Language (XML)
documents, a format that is both human and machine readable. This information
is then used for the purpose of classifying and searching papers in a
human-like way.

It is therefore necessary to define what a 'human-like way' of processing
scientific papers on the internet consists of. Steven Krug is an expert in the field of
human-computer interaction on the internet. In `Don't Make Me Think', Krug
suggests that when browsing the internet, humans find it much easier to locate
specific information within a labelled and logically structured document than
one that is provided as a single text entity.\cite{Krug:2005:DMM:1051204}. In
order to help humans to find relevant research papers, Partridge will represent
all research papers in its repository in a logical hierarchy that can be
queried directly by the human users and also processed using other NLP
techniques to extract further information.

Partridge's document storage format should therefore be formalised to provide a
standard way of processing each document. In their 2007 paper, Soldatova and
Liakata propose a methodology for storing the Core Information about Scientific
Papers (CISP) as a way to formally represent scientific concepts that should be
present in the papers in a logical ontology\cite{soldatova2007ontology}. They
then proceed to define a schema for their CISP ontology that defines the
Core Scientific Concepts (CoreSC) as part of the XML document
itself\cite{liakata2008guidelines}. Using this format for Partridge would allow
the system to read and process the ART corpus produced using CoreSC markup

@@

There are also a number of search and indexing systems that specifically look
for scientific papers as opposed to web pages. One of the most publicised and
well known paper search system is Google Scholar
(\url{http://scholar.google.com}).  As can be seen in Figure
\ref{fig:scholar_basic}, This is an adaptation of Google's general search
engine (discussed above) to specifically index and search scientific papers.
Google also offers advanced query options specific to Scholar that allow
searching by author, year and for words that occur only in the document title
as shown in figure \ref{fig:scholar_advanced}. Whilst this does deal with the
problem of `information overload' and provides even more fine control over the
information returned from searches,  the user is still required to have a very
good idea of what they are looking for in terms of keywords and/or specific
authors. It is possible that a user would not know what they are looking for
until they've seen it. Even if the user has a set of keywords to search for,
they can only search the title of the paper or the content as a whole. This
means that users who want to find a particular phrase within a CoreSC part of
the paper (e.g. only look for this phrase in the `Result' section of the
paper) are unable to get results at their desired level of detail.

@@

Partridge will provide the option to filter papers by subject and it is hoped
that the system will also provide user-specific recommendations by profiling
them through their reading history. This will make it easier for users to find
relevant papers without knowing exactly which keywords they need to search for.
Partridge will also offer facilitate searching for keywords within a specific
CoreSC section by making use of Liaketa et al's SAPIENTA project for
classifying each sentence of paper.
